### 2008-08-01 doc/ws-quick-guide/ws-quick-guide.tex
Remove executable properties from files (windows feature?) and mark binaries as ... binaries

Since the first release (May 2002) the middleware has been deployed and
been used in production environments. Emphasis is put on scalability,
stability, reliability and performance of the middleware. A growing
number of grid projects, like NDGF, Swegrid or Swiss National Grid has
chosen ARC as their middleware.

This document provides a quick usage guide to the new Web Service (WS)
components of ARC, often referred to as ARC1 components. WS design of ARC is
based on a service container -- the Hosting Environment Daemon (HED), and
different grid capabilities are implemented as Web Services residing in HED.

Currently included components are:
\begin{itemize}
\item an OGSA BES~\cite{ogsa-bes} compliant execution service -- \em{ARC
Resource-coupled EXecution service (A-REX)}
\item an echo service (for testing purposes)
\end{itemize}

@@

You can get the latest source code for ARC1 from the Subversion repository. See
\url{http://svn.nordugrid.org} for more details.

@@

\begin{shaded}
\url{http://download.nordugrid.org/software/nordugrid-arc1/nightly/}
\end{shaded}

Choose the latest date available and download snapshot tarball -- for example
\verb|nordugrid-arc1-200802201038-snapshot.tar.gz|.

@@

There are examples of A-REX service and Echo service with Security Handlers
being used. They may be found in
\verb|$ARC_LOCATION/share/doc/arc/arex_secure.xml| and
\verb|$ARC_LOCATION/share/doc/arc/echo.xml|.

@@

Specifically for \texttt{arc.pdp} and \texttt{pdpservice}, a formatted policy
with specific schema should be managed, see
\verb|$ARC_LOCATION/share/doc/arc/pdp_policy.xml.example| and 
\verb|$ARC_LOCATION/share/doc/arc/Policy.xsd| for details.

@@

\begin{shaded}
\url{http://www.nordugrid.org/documents/certificate_howto.html}\\
\url{http://www.nordugrid.org/documents/ng-server-install.html#security}.
\end{shaded}

@@

\begin{shaded}
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/doc/sec/TestCA}
\end{shaded}

@@

\begin{shaded}
\url{https://vls.grid.upjs.sk/CA/instantCA}
\end{shaded}

@@

\texttt{/etc/grid-security/hostcert.pem} \\and\\
\texttt{/etc/grid-security/hostkey.pem}

@@

The open source development of the ARC middleware is coordinated by the
NorduGrid Collaboration. Currently, the main contributor is the KnowARC project
(\url{www.knowarc.eu}), but the Collaboration is open to new members.
Contributions from the community to the software and the documentation is
welcomed. Sources can be downloaded from the software repository at
\url{download.nordugrid.org} or the Subversion code repository at
\url{svn.nordugrid.org}.

The technical coordination group defines outstanding issues that have
to be addressed in the framework of the ARC development. Feature
requests and enhancement proposals are recorded in the Bugzilla bug
tracking system at \url{bugzilla.nordugrid.org}. For a more detailed
description, write access to the code repository and further
questions, write to the \texttt{nordugrid-discuss} mailing list (see
\url{www.nordugrid.org} for details). Ongoing and completed Grid Research
projects and student assignments related to the middleware are listed
on the NorduGrid Web site as well.

@@

User support and site installation assistance is provided via the
request tracking system available at \texttt{nordugrid-support@nordugrid.org}.
In addition, NorduGrid runs a couple of mailing lists, among which the
nordugrid-discuss mailing list is a general forum for all kind of
issues related to the ARC middleware.

Feature and enhancement requests, as well as discovered problems, should be
reported in the Bugzilla problem tracking system \url{bugzilla.nordugrid.org}.

Research papers, overview talks, reference manuals, user guides,
installation instructions, conference presentations, FAQ and even
tutorial materials can be fetched from the documentation section of
\url{www.nordugrid.org}.

Contact information is kept updated on the \url{www.nordugrid.org} Web site.

\bibliography{ws-quick-guide}
\end{document}

>>>>

Since the first release (May 2002) the middleware has been deployed and
been used in production environments. Emphasis is put on scalability,
stability, reliability and performance of the middleware. A growing
number of grid projects, like NDGF~\cite{ndgf}, Swegrid~\cite{swegrid} or Swiss
National Grid Association~\cite{swing} has chosen ARC as their middleware.

This document provides a quick usage guide to the new Web Service (WS)
components of ARC, often referred to as ARC1 components. WS design of ARC is
based on a service container -- the \textit{Hosting Environment Daemon (HED)},
and different grid capabilities are implemented as Web Services residing in HED.

Currently included components are:
\begin{itemize}
\item an OGSA BES~\cite{ogsa-bes} compliant execution service --
\textit{ARC Resource-coupled EXecution service (A-REX)}~\cite{arex}
\item an \textit{Echo} service (for testing purposes)
\end{itemize}

@@

You can get the latest source code for ARC1 from the Subversion repository.
For details, see:

\url{http://svn.nordugrid.org}

@@

\url{http://download.nordugrid.org/software/nordugrid-arc1/nightly/}

Choose the latest date available and download snapshot tarball -- for example\\
\verb|nordugrid-arc1-200802201038-snapshot.tar.gz|.

@@

There are examples of A-REX service and Echo service with Security Handlers
being used. They may be found in:

\verb|$ARC_LOCATION/share/doc/arc/arex_secure.xml| \\and\\
\verb|$ARC_LOCATION/share/doc/arc/echo.xml|.

@@

Specifically for \texttt{arc.pdp} and \texttt{pdpservice}, a formatted policy
with specific schema should be managed, for details see:

\verb|$ARC_LOCATION/share/doc/arc/pdp_policy.xml.example| \\and\\
\verb|$ARC_LOCATION/share/doc/arc/Policy.xsd|

@@

\url{http://www.nordugrid.org/documents/certificate_howto.html}\\
\url{http://www.nordugrid.org/documents/ng-server-install.html#security}

@@

\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/doc/sec/TestCA}

@@

\url{https://vls.grid.upjs.sk/CA/instantCA}

@@

\verb|/etc/grid-security/hostcert.pem| \\and\\
\verb|/etc/grid-security/hostkey.pem|

@@

The open source development of the ARC middleware is coordinated by the
NorduGrid Collaboration. Currently, the main contributor is the KnowARC
project~\cite{knowarc}, but the Collaboration is open to new members.
Contributions from the community to the software and the documentation is
welcomed. Sources can be downloaded from the software repository at:

\url{http://download.nordugrid.org}

or the Subversion code repository at

\url{http://svn.nordugrid.org}.

The technical coordination group defines outstanding issues that have
to be addressed in the framework of the ARC development. Feature
requests and enhancement proposals are recorded in the Bugzilla problem
tracking system at:

 \url{http://bugzilla.nordugrid.org}

For a more detailed description, write access to the code repository and
further questions, write to the \texttt{nordugrid-discuss} mailing list (see
NorduGrid Web site~\cite{nordugrid} for details). Ongoing and completed Grid
Research projects and student assignments related to the middleware are listed
on the NorduGrid Web site as well.

@@

User support and site installation assistance is provided via the
request tracking system available by e-mail to
\texttt{nordugrid-support@nordugrid.org}.
In addition, NorduGrid runs a couple of mailing lists, among which the
nordugrid-discuss mailing list is a general forum for all kind of
issues related to the ARC middleware.

Feature and enhancement requests, as well as discovered problems, should be
reported in the Bugzilla problem tracking system
(\url{http://bugzilla.nordugrid.org}).

Research papers, overview talks, reference manuals, user guides,
installation instructions, conference presentations, FAQ and even
tutorial materials can be fetched from the documentation section of the
NorduGrid Web site.

Contact information is kept updated on the NorduGrid Web site.

\bibliography{grid}
\end{document}
